Assessing glymphatic transport velocities by adjoint methods

### 2018-10-07 tex/paper.tex
update
Lagt til bilder

\section*{Implementation}
The code used the FEniCS project to solve the PDE, using backwards Euler time discretization and first order continuous Galerkin finite elements. The module dolfin adjoint ~\cite{farrell2013automated} \kam{correct ref?} was used to solve the PDE constrained optimization problem via  using L-BFGS-B algorithm via scipy.

@@

The times in the forward simulation do not always overlap with observations times. Thus a linear interpolation of the forward problem was used to compute the difference from the observation, i.e 
\begin{equation}
u_{linear} = \frac{\Delta t}{dt} U_prev + \frac{dt - \Delta t }{dt} U.
\end{equation}
Here $dt$ is forward timestep and $\Delta t$ is the difference between observation time and forward time. \kam{This has to be made clearer. Earlier we used $u_{obs}$ for observation. Also this also only applies if $t_i$ is close to the observations, right?} 
The initial values of the optimization algorithm was chosen to be $1,1,1$. Furthermore, to obtain faster convergence in the optimization, the diffusion coefficients was scaled to have the same magnitude, i.e.  $D_{\Omega_1}$ was scaled, so that $D_{\Omega_1} = D\sp {s}_{\Omega_1}100$.

@@

The real data observations had observation times that had an unevenly distribution over 24 hours. Thus having  constant time between observations is not realsitic. Therefore the number of observation and the unevenly distribution of them will be tested. To accurately depict the real data observations.

@@

@@

Noen detaljer her om element methode, optimerings algoritme, prekondisjonering
grid, osv.

@@

>>>>

\section*{Implementation}

The code used the FEniCS project to solve the PDE, using backwards Euler time discretization and first order continuous Galerkin finite elements. The module dolfin adjoint ~\cite{farrell2013automated} \kam{correct ref?} was used to solve the PDE constrained optimization problem with the L-BFGS-B algorithm via scipy.

@@

The observations $u_{obs}$ have fixed time-points $t_i$, these time-points may not correspond to the time discretization in the forward problem. Therefore, after each time step $dt$ in Eq\ref{Eq::PDE}, it was checked if the time step contained the next observation. If it did, then a linear interpolation of the current solution $u$ and previous solution $u_prev$ was used approximate the solution corresponding to $t_i$. The linear interpolation was given as  
\begin{equation}
u_{linear} = \frac{\Delta t}{dt} U_{prev} + \frac{dt - \Delta t }{dt} U,
\end{equation}
with $\Delta t$ is the difference between observation time and the time in the forward problem.

 \kam{This has to be made clearer. Earlier we used $u_{obs}$ for observation. Also this also only applies if $t_i$ is close to the observations, right?}

The initial values of the optimization algorithm was chosen to be $1,1,1$. Furthermore, to obtain faster convergence in the optimization, the diffusion coefficients was scaled to have the same magnitude, i.e.  $D_{\Omega_1}$ was scaled, so that $D_{\Omega_1} = D\sp {s}_{\Omega_1}100$.

@@

The real data observations had observation times that had an unevenly distribution over 24 hours. Thus having  constant time between observations is not realistic. Therefore the number of observation and the unevenly distribution of them will be tested. To accurately depict the real data observations.

@@

\kam{check that all symbols are explained here}

@@

\kam{
Noen detaljer her om element methode, optimerings algoritme, prekondisjonering
grid, osv. 
}

The gird

@@

\begin{figure}
\centering
\includegraphics[scale=0.2]{27-12-hours-scale-0-1-3.png}  
\caption{The upper row shows the manufactured observation, A ) Shows the manufactured observation at time-point 24 with no noise added. B) Shows the manufactured observation at time-point 24 with an noise amplitude of 0.15 {\color{red} explain noise amplitude}. C)Shows the manufactures observation at time-point 24 with noise amplitude of 0.3. The lower row shows the results with optimized parameter obtained with $alpha=0.0001$, $\beta=1.0$ and $k=27$. D) Shows the  . E)  Shows the  F)  Shows the  }
\end{figure}

\begin{figure}
\centering
\includegraphics[scale=0.2]{27-24-hours-scale-0-1.png}
\caption{The upper row shows the manufactured observation, A ) Shows the manufactured observation at time-point 24 with no noise added. B) Shows the manufactured observation at time-point 24 with a noise amplitude of 0.15 {\color{red} explain noise ampliutde}. C)Shows the manufactures observation at time-point 24 with noise amplitude of 0.3. The lower row shows the results with optimized parameter obtained with $alpha=0.0001$, $\beta=1.0$ and $k=27$. D) Shows the  . E)  Shows the  F)  Shows the  }
\end{figure}
